A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-09-17 paper/paper.discussion.tex
Minor fix to discussion

In this paper, we present a simple, yet flexible, integer linear programming
formulation to generate schedules for clinical departments at hospitals.
The challenge in applying ILP to the task of scheduling clinicians lies in the
computational complexity of finding an optimal solution. As the size of the
% JK: Is this a challenge of applying ILP? Or of the problem in general?
%     I got the impression that ILP was a nice way to overcome this problem.
scheduling problem grows, due to a larger roster of clinicians or more
complicated constraints, the time it takes to generate an optimal schedule may
grow exponentially.
%The challenge in applying such an approach to this task lies in the fact that
%ILP is an NP-hard problem. %specify what 'such an approach' and 'this task'
%are... the first part of the sentence was a bit hard to follow. Define what you
%mean by NP-hard problem and cite --> i.e. NP-hard = the following sentence
%about how time to optimal solution grows exponentially? if yes, then instead of
%'As such' - say 'That is,...or "An NP-hard problem means that..."
% JK: How come only "may"? Under what conditions?
As a result, the majority of approaches taken to create schedules for similar
scenarios tend to use heuristics in order to find an approximately optimal
solution in a shorter time~\cite{burke_state_2004}. %cite/reference
%statement (i.e. the 'vast majority'...) I can't remember if the introduction
%details the heuristics --> but if yes, then great. if no, then include that
%review of the prior literature here in discussion. I think as you said - the
%journals we are submitting to seem to have more of those details in the
%introduction.

>>>>

In this paper, we present a simple, yet flexible, integer linear programming
formulation to generate schedules for clinical departments at hospitals.
The challenge in applying ILP to the task of scheduling clinicians lies in the
computational complexity of finding an optimal solution. As the size of the
% JK: Is this a challenge of applying ILP? Or of the problem in general?
%     I got the impression that ILP was a nice way to overcome this problem.
scheduling problem grows, due to a larger roster of clinicians or more
complicated constraints, the time it takes to generate an optimal schedule may
grow exponentially in the worst case.
%The challenge in applying such an approach to this task lies in the fact that
%ILP is an NP-hard problem. %specify what 'such an approach' and 'this task'
%are... the first part of the sentence was a bit hard to follow. Define what you
%mean by NP-hard problem and cite --> i.e. NP-hard = the following sentence
%about how time to optimal solution grows exponentially? if yes, then instead of
%'As such' - say 'That is,...or "An NP-hard problem means that..."
% JK: How come only "may"? Under what conditions?
As a result, the majority of approaches taken to create schedules for similar
scenarios tend to use heuristics in order to find an approximately optimal
solution in a shorter time~\cite{burke_state_2004}. %cite/reference
%statement (i.e. the 'vast majority'...) I can't remember if the introduction
%details the heuristics --> but if yes, then great. if no, then include that
%review of the prior literature here in discussion. I think as you said - the
%journals we are submitting to seem to have more of those details in the
%introduction.
